This is the title [Article v\versionnumber]

### 2022-03-17 manuscript/manuscript.tex

Now, you can finally run the actual GIST analysis. Center the molecule exactly in the same way as above, to make sure that its position matches the grid parameters that you decided on.
We recommend using either the PME or GPU implementation of GIST, depending on whether you have a fast GPU.
A further advantage of the PME implementation is that it matches the energy calculation of the MD engine more closely.
\todo{At the time of writing, it is important to use an up-to-date version of PME-GIST, or the Esw-Eww decomposition will not be available. Maybe remove this for the final version, when Amber22 is out.}
\begin{lstlisting}
parm solvated.parm7
trajin md-01.nc
autoimage !(:WAT) origin
# remove the "pme" option if you want to use the GPU
gist griddim 100 100 100 out gistoutlong.dat \
  refdens 0.03287 pme
# other settings you might want to change
# (those are the defaults)
# gridcntr 0 0 0 gridspacn 0.5 temp 300
\end{lstlisting}
\subsection{Reference Values and Radial Convergence}
\subsection{Visualizing $\dgsolv$}
\subsection{Contribution of Hydration to Binding}

>>>>

Now, you can finally run the actual GIST analysis. Center the molecule exactly in the same way as above, to make sure that its position matches the grid parameters that you decided on.
We recommend using either the PME or GPU implementation of GIST, depending on whether you have a fast GPU.
A further advantage of the PME implementation is that it matches the energy calculation of the MD engine more closely.
\todo{At the time of writing, it is important to use an up-to-date version of PME-GIST, or the Esw-Eww decomposition will not be available. Maybe remove this for the final version, when Amber22 is out.}
\begin{lstlisting}
parm solvated.parm7
trajin md-01.nc
autoimage !(:WAT) origin
# remove the "pme" option if you want to use the GPU
gist griddim 100 100 100 out gist.dat \
  refdens 0.03287 pme
# other settings you might want to change
# (those are the defaults)
# gridcntr 0 0 0 gridspacn 0.5 temp 300
\end{lstlisting}
\subsection{Reference Values and Radial Convergence}
All GIST quantities should be expressed relative to bulk. In practice, this is not problematic for the entropies, since they are computed relative to a distribution of randomly oriented molecules at the reference density.
The solute-solvent energy Esw is also no problem, because it naturally tends to zero in bulk. 
However, the solvent-solvent energy Eww needs to be referenced.

The Amber manual provides reference energies for several solvents.
However, the exact reference value is different when using PME-GIST, and also depends on the box size.
For exact analyses such as computing the total $\dgsolv$ of a compound, it is important to compute an exact reference energy.

The most accurate method to compute a reference energy is to run a separate GIST calculations with the same energy method (PME/GPU) and a similar box size, and then compute the average solvent-solvent energy per molecule.

\begin{equation}
\label{eq_ewwref}
E_{ww}^\textit{ref} = \frac{\int{E_{ww}} \mathrm{d}x}{\left<N_\textit{solvent}\right>}
  = \frac{\sum_\textit{voxels}E_{ww}^\textit{dens} V_\textit{vox}}{\sum_\textit{voxels}{N_\textit{solvent}} / N_\textit{frames}}
\end{equation}

Alternatively, one can note that the solvent-solvent energy in a sufficiently large GIST grid converges to the correct bulk value at large distance to the solute.
This means that the reference energy can be obtained from a large GIST grid by binning the voxels by their distance to the solute, and evaluate Equation \ref{eq_ewwref} within each bin.
If this value converges to a constant, this can be used as $E_{ww}^\textit{ref}$.

\software{gisttools} contains functionality to perform this analysis easily.
There is also a method ``detect\_reference\_value'' that automatically tries to find the converged value fo the rdf.
Although it has a simple convergence check built-in, it is always recommended to check the convergence by hand as well.

\begin{lstlisting}[style=python]
import gisttools as gt
import matplotlib.pyplot as plt
gist = gt.gist.load_gist_file(
    "gist.dat", struct="solute-centered.pdb")
bins, eww = gist.rdf("Eww_unref", bins=100, rmax=20.)
_, n = gist.rdf(
    "population", bins=100, rmax=20., col_suffix="")
plt.plot(
    bins,
    eww / (n/gist.n_frames/gist.grid.voxel_volume))
eww_auto = gist.detect_reference_value().values[0]
plt.axhline(eww_auto, color='k')
plt.gca().set(
    xlabel='distance [A]', ylabel='E_ww per mol')
plt.show()
\end{lstlisting}

The expected output of this code is shown in Figure \ref{fig_ewwref}.

\begin{figure}
	\centering
	\includegraphics[width=0.8\linewidth]{figures/Eww_convergence.eps}
	\caption{Convergence of $E_{ww}$ with increasing distance to the solute. The horizontal line shows the automatically computed reference energy.}
	\label{fig_ewwref}
\end{figure}

\subsection{Visualizing $\dgsolv$}
\subsection{Contribution of Hydration to Binding}
